Effects of epidemiological structure on the transient evolution of HIV virulence

### 2017-01-15 ms/ms.tex
bring diagram subfigure structure into main ms

@@

\begin{figure}[!ht]
\includegraphics[width=\textwidth]{../figures/diagrams_panel.pdf}
\caption{{\bf Model contact structures.} 
Schematic representations of models with
explicit contact structure. Top row (a,b) shows models with instantaneous
partnership formation; bottom row (c,d)  shows those where individuals remain
single for some period of time between partnerships. Left column (a,c) 
shows models with within-partnership transmission only; in these models
transmission can only occur within serodiscordant partnerships, and
serodiscordant partnerships can only be formed by dissolution
and reformation of partnerships. Right column (b,d) shows models
that allow extra-pair and uncoupled transmission.
\emph{Solid arrows} represent infection transitions; \emph{dotted arrows}
represent partnership dissolution and formation; \emph{dashed arrows}
show influences on infection rate, including both within-pair
transmission (blue) and extra-pair/uncoupled transmission (red).
In addition to these models, we also use random-mixing and implicit
models with only $S$ and $I$ compartments and heterogeneous models
where each compartment is subdivided by sexual activity rate
(of both partners, in the case of partnership compartments).
}
\label{fig:diagrams}
\end{figure}

>>>>

\usepackage{subcaption}

@@

\begin{figure}[t!p]

\begin{subfigure}[b]{0.4\linewidth}
	\centering
	\raisebox{0.44\height}{
	  \includegraphics[width=0.9\linewidth]{../figures/tikz-f1}
	}
\caption{Instantaneous switching without extra-pair contact (``instswitch'')}
\end{subfigure}
\begin{subfigure}[b]{0.4\linewidth}
	\centering
	  \includegraphics[width=0.9\linewidth]{../figures/tikz-f2}
\caption{Instantaneous switching with extra-pair contact (``instswitch+epc'')}
\end{subfigure}

\begin{subfigure}[b]{0.4\linewidth}
	\centering
	\raisebox{0.33\height}{
	  \includegraphics[width=0.9\linewidth]{../figures/tikz-f3}
	}
\caption{Pair-formation model without extra-pair/uncoupled contact 
(``pairform'')}
\end{subfigure}
\begin{subfigure}[b]{0.4\linewidth}
	\centering
	  \includegraphics[width=0.9\linewidth]{../figures/tikz-f4}
\caption{Pair-formation model with extra-pair/uncoupled contact
(``pairform+epc'')}
\end{subfigure}

\caption{{\bf Model contact structures.} 
Schematic representations of models with
explicit contact structure. Top row (a,b) shows models with instantaneous
partnership formation; bottom row (c,d)  shows those where individuals remain
single for some period of time between partnerships. Left column (a,c) 
shows models with within-partnership transmission only; in these models
transmission can only occur within serodiscordant partnerships, and
serodiscordant partnerships can only be formed by dissolution
and reformation of partnerships. Right column (b,d) shows models
that allow extra-pair and uncoupled transmission.
\emph{Solid arrows} represent infection transitions; \emph{dotted arrows}
represent partnership dissolution and formation; \emph{dashed arrows}
show influences on infection rate, including both within-pair
transmission (blue) and extra-pair/uncoupled transmission (red).
In addition to these models, we also use random-mixing and implicit
models with only $S$ and $I$ compartments and heterogeneous models
where each compartment is subdivided by sexual activity rate
(of both partners, in the case of partnership compartments).
}
\label{fig:diagrams}
\end{figure}
